Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-10 journal/content.tex
Layout fix
Conclusion section

\begin{table}[t]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.61\textwidth}
                     >{\raggedright\arraybackslash}p{0.31\textwidth} }
        \toprule
        Challenges in requirements engineering and quality assurance  &  Described in \\
        \midrule
        How to accommodate high level requirements management  &  P24, P31, P39, P45, P51  \\
        Problems with breakdown of requirements        &  P1, P17, P33, P48  \\
        Creating and estimating user stories is hard   &  P5, P11, P27, P30, P33, P37 \\
        Handling coexisting long and short term planning  &  P9, P10, P13, P26, P31, P38 \\
        Accommodating performance, load, and memory testing  &  P17, P28, P31, P48 \\
        Lack of automated testing slows down           &  P10, P11, P17 \\
        New requirements management practices affect QA  &  P5, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of requirements engineering and quality assurance related
             challenges relating in the agile model}
    \label{table:challenges_requirementsandqa}
\end{table}

@@

A concluding overview.

* Recap of the work

* Recap of most important results

(* Future research?)

>>>>

\begin{table}[!b]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.61\textwidth}
                     >{\raggedright\arraybackslash}p{0.31\textwidth} }
        \toprule
        Challenges in requirements engineering and quality assurance  &  Described in \\
        \midrule
        How to accommodate high level requirements management  &  P24, P31, P39, P45, P51  \\
        Problems with breakdown of requirements        &  P1, P17, P33, P48  \\
        Creating and estimating user stories is hard   &  P5, P11, P27, P30, P33, P37 \\
        Handling coexisting long and short term planning  &  P9, P10, P13, P26, P31, P38 \\
        Accommodating performance, load, and memory testing  &  P17, P28, P31, P48 \\
        Lack of automated testing slows down           &  P10, P11, P17 \\
        New requirements management practices affect QA  &  P5, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of requirements engineering and quality assurance related
             challenges relating in the agile model}
    \label{table:challenges_requirementsandqa}
\end{table}

@@

The goal of this work was to review and analyze empirical studies of large
organizations taking agile software development methods into use. By applying
the method of systematic literature review we analyzed the findings of 52
studies describing the agile transformation in 40 different organizations. As a
result we presented qualitative findings describing typical reasons to change,
characteristics of transformations, challenges, and success factors.

The primary motive to change was a demand to faster and more flexibly respond to
business needs. Other reasons included the desire to mitigate known problems in
the organization.
Transformation processes could be characterized along two dimensions,
one distinguishing between top-down and bottom-up leadership, and the other
being the transformation velocity. Typical characteristics in transformations
were use of pilot projects, bringing in external consultants, and investing in
training.

Typical challenges included change resistance and lack of commitment and
investment in transformation. Some challenges related particularly to large
scale, such as implementing effective coordination between teams, and friction
caused by the fact that a large organization can not transform all at once.
The most important success factors were management support, use of training and
coaching and carefully customizing the agile model to fit the organization.

Where to from here?
Adopting agile methods in large organizations is closely related to generic
discussion on organizational change. A possible direction for future research
would be to compare the agile transformations to research on change in knowledge
organizations from the viewpoint of organizational research. The organizational
research domain is significantly older than research on agile development, and
would therefore likely provide additional insight in agile transformations.
Also, agile methods and organizations using them mature over time. A research
topic related to transformation is the follow-up of the evolving agile process.
Research seems to be scarce on the evolving of agile methods after introduction
in large organizations.
